% !TEX TS-program = LuaLaTeX
\documentclass[margin,line]{resume}

\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{setspace}
\usepackage{enumitem}

\begin{document}
\name{\huge\hfill\hspace{-2.3cm}JONATHAN THOMAS\hfill\vspace{3.5mm}}       
\begin{resume}
	\vspace{-3.5mm}
	\section{\mysidestyle Contact\\Info}
	\noindent 
		\faEnvelope \hspace{1mm} \href{mailto:jonthoma@umich.edu}{\nolinkurl{jonthoma@umich.edu}} \hfill% / {\nolinkurl{jonthoma@umich.edu}}  
		\faLinkedinSign \hspace{1mm} \href{https://linkedin.com/in/jonathoma}{\nolinkurl{jonathoma}}\\
	\noindent 
		\faPhone \hspace{1mm} \nolinkurl{(XXX)-XXX-XXXX} \hfill 
		\faUser \hspace{1mm} \href{https://jonathoma.github.io}{\nolinkurl{jonathoma.github.io}} \\ 
		%\faHome : \ttfamily{2511 Black Horse Dr NE, Grand Rapids, MI 49505}\rmfamily \hfill  
		%\faGithub : \href{https://github.com/jonathoma}{\nolinkurl{github.com/jonathoma}} \\ 
	\vspace{-2.5mm}
	    
	%\sectionbreak
	%\section{\mysidestyle Objective}
	%Seeking a full-time backend software engineering position specializing in distributed systems for Fall 2019. \\
	%\vspace{-1.5mm}
	
	\sectionbreak
	\section{\mysidestyle Education}
	
	\textbf{University of Michigan \hfill Ann Arbor, MI} \\\vspace{1mm}%
	\textsl{B.S.E. Computer Science and Honors Mathematics, Philosophy Minor} \hfill \textsl{Grad. May 2019}\vspace{-1mm}\\
	\textbf{GPA: 3.85 / 4.00} \\\vspace{-2.5mm}%
	\begin{itemize}[leftmargin=4mm]
		\item Engineering Scholarship of Honor, Regents Merit Scholarship, National Merit Scholar
		\item William J. Branstrom Freshman Prize, University Honors / Dean's List (all semesters)
		\item Coursework: Operating Systems, Computer Networks, Compiler Construction, Machine Learning
	\end{itemize}
	%\vspace{-6mm}
	%\begin{center}\hspace{-2.3cm}\textbf{Coursework}\end{center}
	%\vspace{-4mm}
	%\small
	%\begin{itemize}[leftmargin=4mm]
	%	\begin{minipage}[t]{.6\linewidth}
	%		\item Operating Systems (EECS 482)
	%		\item Object Oriented and Advanced Programming (EECS 381)
	%		\item Computer Networks (EECS 489)
	%	\end{minipage}%
	%	\begin{minipage}[t]{.5\linewidth}
	%		\item Compiler Construction (EECS 483)
	%		\item Machine Learning (EECS 445)
	%		\item Web Systems (EECS 485)
	%	\end{minipage}%
	%\end{itemize}
	%\normalsize
	\vspace{1.5mm}

	\sectionbreak
	\section{\mysidestyle Experience}
	
	\textbf{Facebook \hfill New York, NY} \\\vspace{1mm}%
	\textsl{Incoming Software Engineer} \hfill \textsl{Sep 2019}
	\begin{itemize}[leftmargin=4mm]
		\item Incoming new graduate software engineer at Facebook NY.
	\end{itemize}
	\vspace{-1.5mm}
	
	\textbf{Facebook \hfill Menlo Park, CA} \\\vspace{1mm}%
	\textsl{Software Engineering Intern - Kernel Applications} \hfill \textsl{Summer 2018}
	\begin{itemize}[leftmargin=4mm]
		\item Designed and implemented C\texttt{++} service to dynamically create, destroy, list and retrieve status of network block devices used in Facebook's disaggregated flash storage.
		\item Improved Python block storage allocation service to support pushing notifications of updates  instead of clients polling for updates as an independent microservice.
		\item Wrote tool to override command line options based on customizable host and data center configurations; reduced workflow for testing new application versions.
		\item Removed internal Facebook dependencies in the process of open sourcing the oomd \href{https://github.com/facebookincubator/oomd}{\faGithub} project. 
	\end{itemize}
	\vspace{-1.5mm}
	
	\textbf{J.P. Morgan Chase Digital \hfill New York, NY} \\\vspace{1mm}%
	\textsl{Software Engineering Intern - Digital Authentication} \hfill \textsl{Summer 2017}
	\begin{itemize}[leftmargin=4mm]
		\item Wrote Java code to unify separate interfaces for Chase account backend services, streamlining testing.
		\item Performed code quality inspection with senior colleagues for Java code with suggestions for refactoring, eliminating duplicated code and applying proper object-oriented design patterns.
		\item Wrote tests for new protocol incorporating OAuth token authorization for 3rd-party aggregators.
	\end{itemize}
	
	%\vspace{-1.5mm}
	%\textbf{Department of Mathematics \hfill Ann Arbor, MI} \\\vspace{1mm}%
	%\textsl{Proof Tutor} \hfill \textsl{Fall 2016 -- Present}
	%\begin{itemize}[leftmargin=4mm]
	%	\item Guide students in demonstrating rigorous proofs of fundamental theorems in linear algebra.
	%\end{itemize}
	\vspace{1.5mm}
	
	\sectionbreak
	\section{\mysidestyle Projects}
	%\textbf{Personal Website -} \href{https://jonathoma.github.io}{\nolinkurl{jonathoma.github.io}}  \hfill \textsl{Summer 2017}
	%\begin{itemize}[leftmargin=4mm]
		%\item Created website to host personal projects and general information about me. Gained exposure to HTML, CSS and basic web development.
	%\end{itemize}
	%\vspace{-2.5mm}
	%\textbf{Project Euler}  \hfill \textsl{Summer 2017}
	%\begin{itemize}[leftmargin=4mm]
		%\item Solved Project Euler problems 1 - 100 in Haskell to learn more about functional programming.
	%\end{itemize}
	%\vspace{-2.5mm}
	
	\textbf{Engineering Honors Capstone \href{https://github.com/jonathoma/js-correctness-checker}{\faGithub} \hfill Ann Arbor, MI} \\\vspace{1mm}%
	\textsl{Undergraduate Researcher} \hfill \textsl{Winter 2019}
	\begin{itemize}[leftmargin=4mm]
		\item Building a command line tool to assist in checking correctness in the DOM trees and memory heaps of cached JavaScript function executions under faculty advisor Prof. Harsha Madhyastha.
		%\item Working with Node.js . 
	\end{itemize}
	\vspace{-1.5mm}
	
	\textbf{Laboratory of Geometry \href{https://github.com/jonathoma/LogM}{\faGithub} \hfill Ann Arbor, MI} \\\vspace{1mm}%
	\textsl{Undergraduate Researcher} \hfill \textsl{Fall 2017}
	\begin{itemize}[leftmargin=4mm]
		\item Investigated the combinatorics of the Mandlebrot set under faculty advisor Prof. Sarah Koch.
		\item Wrote Python scripts using SageMath, numpy and matplotlib to visualize associated data and help with symbolic algebra computations. 
	\end{itemize}
	
	%\vspace{-1.5mm}
	%\textbf{Song of the Day \href{https://github.com/jonathoma/songoftheday}{\faGithub}}  \hfill \textsl{Summer 2017} \vspace{1mm}%
	%\begin{itemize}[leftmargin=4mm]
	%	\item Used Python scripts in conjunction with Spotify and Last.fm APIs to provide myself with a daily-updated, personalized song recommendation on my website \href{https://jonathoma.github.io}{\nolinkurl{jonathoma.github.io}} .
	%\end{itemize}
	\vspace{1.5mm}
	
	\sectionbreak
	\section{\mysidestyle Leadership}
	\textbf{Engineering Honors Program \hfill Ann Arbor, MI} \\\vspace{1mm}%
	\textsl{President, Honors Student Advisory Board} \hfill \textsl{March 2017 - Present}
	\begin{itemize}[leftmargin=4mm]
		\item Lead the planning of events and opportunities that help strengthen and grow the Honors community.
		\item Manage and schedule weekly meetings of the board for the term.
		%\item Serve as main liaison between Honors students, faculty, staff and alumni.
	\end{itemize}
	
	\vspace{1.5mm}
	
	\sectionbreak
	\section{\mysidestyle Activities}
	\begin{flushright}
		\vspace{-7.5mm}
		\textsl{Assistant Concertmaster}, Michigan Pops Orchestra  \hfill \textsl{Sep 2015 - Present}\\
		Honors GO! New Zealand Volunteer \hfill \textsl{April - May 2017} \\
		%Michigan Math Club \hfill \textsl{Sep 2015 - Present}
	\end{flushright}
	\vspace{-1.5mm}
	    
	\sectionbreak
	\section{\mysidestyle Skills}
	Languages: C\texttt{++}, C (main), Python (proficient), Java (familiar) \\ %Haskell (familiar) \\
	Other Technologies: Bash, Git, \LaTeX, Vim \\
	% \emph{Foreign Languages:} Spanish (proficient) \\
	Miscellaneous:  Avid music listener, vinyl and book collector, veteran game night host
\end{resume}
\end{document}